---
title: "Harvard Data Science Capstone"
author: "Tyson Klein"
date: "October 22, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Analysis of RedBubble.com sales by TysonK

##An Overview

RedBubble is one of the longest running and diverse Print-On-Demand (POD) art websites in the world, offering artists everywhere a chance to make money by selling their works on a range of products without having to get involved with any of the logistics. As a homebody with a penchant for Photoshop, I was naturally drawn to it.

Redbubble, like many of its contemporaries, has a 'passive' approach for the artist. You upload your designs as images, and they do everything else. This means that all sales made are pure profit on the artists side.

About a year and a half ago I opened [my Redbubble store](https://www.redbubble.com/people/tysonk?ref=account-nav-dropdown&asc=u). The specifics of my store aren't entirely important to this report, but there are some important details that will emerge again later. Most designs I uploaded had something to do with National Parks from English speaking countries around the world, and the remainder of the designs are an eclectic mix of outdoors-themed and quirky pruducts meant to appeal to a general audience.

The money started to come in, and as I tweaked some designs and parameters within my store, I realized that this could be a legitimate income stream. Beyond that, some interesting patterns began to emerge. For example, although Redbubble offers designs to be printed on products ranging from coffee mugs to T shirts to throw pillows, by far my most sucessfull item was the sticker.

To date, stickers account for 98.5% of all items sold and 96.2% of all revenue.

Below is the profit per day of my store since May 1st, 2017, measured in Canadian Dollars(red), and the same graph instead measuring daily items sold (blue).
```{r daily sales plot,fig.align='center',  echo = FALSE}
load("rda/daily-sales-plot.rda")
daily.sales.plot
```

```{r daily units plot,fig.align='center', echo = FALSE}
load("rda/daily-units-plot.rda")
daily.units.plot
```


```{r Monthly plot,fig.align='center', echo = FALSE}
load("rda/MC-boxPlot.rda")
MC.boxPlot
```
